---
title: "BS1808 Logistics and Supply Chain Analytics Group Assignment One"
author: "Jone Leung, Somto Okoye, Valentin Poirelle, Jin Anne Lee, Jim Leach, Niccolo Valerio"
date: '`r Sys.Date()`'
output:
  html_document:
    code_folding: hide
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
---

<br>
<br>
<p style="border:1.5px; border-style:solid; border-color:#000000; padding: 1em;">The Excel sheets used to perform this analysis has been attached to the submission of this report. This `HTML` report is best viewed using a modern web browser such as Mozilla Firefox or Google Chrome. It is also available on the [online repository](https://github.com/Jim89/lsca_group). Printing is possible but will not produce an optimal reading experience.</p>

# Introduction

## Project overview

In this project we have analysed data from _Sport Obermeyer_, a global skiwear company. We have used forecasts of demand for a range of Obermeyer's products in order to determine how many of each style to order. We have considered ordering policies based on ordering from both Hong Kong and China, and have developed a measure of risk in each case. Finally, we have considered operational changes that Obermeyer may wish to consider making, and made proposals for their short and long term sourcing strategies.  

```{r prep, echo = TRUE, message=FALSE}
# Set default knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

# Load packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(purrr)
library(readxl)

# Set up theme object for prettier plots
theme_jim <-  theme(legend.position = "none",
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.text.x = element_text(size = 12, colour = "black"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 16),
    title = element_text(size = 16),
    strip.text = element_text(size = 12, colour = "black"),
    strip.background = element_rect(fill = "white"),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.minor.y = element_line(colour = "lightgrey", linetype = "dotted"),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
    panel.margin.y = unit(0.1, units = "in"),
    panel.background = element_rect(fill = "white", colour = "lightgrey"),
    panel.border = element_rect(colour = "black", fill = NA))

# Function that takes a string and converts it in to "proper case" (i.e.
# the first letter is capitalised, all remaining letters are lower case)
# N.b. for multi-word strings, only the first word will be affected
toproper <- function(x) { 
  first <- substring(x, 1, 1) %>% toupper()
  rest <- substring(x, 2) %>% tolower()
  whole <- paste0(first, rest)
  return(whole)
}
```

# Simulating demand

Each of the 10 styles of Parka under consideration for production had demand forecasts made for them by members of the Obermeyer team. For each style, Obermeyer assumed that the _true_ demand value could be modelled as a random number from the [normal distribution](https://en.wikipedia.org/wiki/Normal_distribution) with a mean given by the average of the individuals' forecasts, and a standard deviation equal to _twice_ the standard deviation of all individuals' forecasts. The individual forecasts, and the resulting mean and standard deviation values for the true demand distributions, are displayed in table one. 

```{r show_raw}
# Get raw demand data
raw <- read_excel("./jim/optim.xlsx", sheet = "Raw")

raw %>% 
    select(1, 3:11) %>% 
    arrange(Style) %>% 
    kable(col.names = c("Style", "Laura", "Carolyn", "Greg", "Wendy", "Tom", "Wally", "Mean", "SD", "SD x2"),
          caption = "Table One: Demand forecasts for each style",
          format.args = list(big.mark = ","))
```

Using these values we generated 1000 estimates of demand for each style from a normal distribution with a mean and standard deviation as described above. The distributions of these 1000 estimates for each parka are displayed in figure 1. Note, figure 1 graphs 90 degree - flipped and mirrored - density plots.

```{r plot_demand, out.height = 1000, out.width=800, fig.cap="Figure 1: Demand estimate distribution for each parka style."}
# Get sampled demand data
demand <- read_excel("./jim/optim.xlsx", sheet = "Demand")

# Create plot
demand %>% 
    select(-3, -4) %>% 
    gather(sample, demand, -Style, -Average) %>% 
    ggplot(aes(x = Style, y = demand, fill = Style)) +
    geom_violin() +
    scale_y_continuous(labels = scales::comma) +
    scale_fill_brewer(palette = "Paired") +
    ylab("Demand (units)") +
    theme_jim +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.65))
```

We then used these demand data in a Monte-Carlo analysis to decide on how much of each style to order.

```{r get_results}
quant <- read_excel("./jim/optim.xlsx", sheet = "OrderQuantities")
profits <- read_excel("./jim/optim.xlsx", sheet = "Profit")
```

# Ordering with no minimum

Initially, we considered a situation in which there were no minimum order requirements. That is, Obermeyer could order any amount of each style that they wished. However, from the 10 styles they had to order at least 10,000 in aggregate. We ignored price and production cost differences across the styles. 

In order to do so, we defined a formula that provided an expectation of the profit for a given quantity of each style:

\begin{equation}
\mbox{Profit} (\Pi_q) = \sum_{j=1}^{10}\bigg[ \frac{1}{n} \sum_{i=1}^n \Big[p.d_{ij} + s    .\max(Q_j - d_{ij}, 0) - c.\max(Q_j, d_{ij})\Big] \bigg]
\end{equation}

Where:

* $Q_j$ is the quantity of style $j$ to produce;
* $p$ is the sale price;
* $s$ is the outlet/markdown price;
* $c$ is the cost of production; and 
* $d_{ij}$ is the $i$^th^ demand value for style $j$.

We note that this is not the standard formula for profit when determining optimal order quantity. This is because Obermeyer only have to produce 10,000 units now and can produce the rest later. Therefore sales revenue is a function of the actual demand realised and not dependent on the current order quantity. However, the (final) cost of production may change (in the future) if more/less of each style is produced now relative the actual demand realised. Hence the first and third terms in the inner summation differ slightly from the standard formula.

Having defined this function, we then used the `Excel` solver to find the optimum order quantity for each style, $Q_j^*$ via the following optimisation program:

\begin{equation} 
\begin{split}
\max_{Q} \mathbb{E} (\Pi_q) \\
\text{s.t.} \\
\sum_{j=1}^{10} Q_j \geq 10000 \\
Q_j \geq 0
\end{split}
\end{equation}

## No minimum order results

The resulting solution from the `Excel` solver, including both order quantity and expected profit for each style is displayed in table 2. 

```{r show_q1}
quant %>% 
    select(1, 2) %>% 
    left_join(profits, by = c("style" = "style")) %>% 
    select(1, 2, 3) %>% 
    kable(col.names = c("Style", "Order Quantity", "Expected Profit ($)"),
          caption = "Table 2: Order quanties and expected profits for each style with no minimum order requirements",
          format.args = list(big.mark = ","))
```

Under this scheme, total profit was expected to be `r scales::dollar(sum(profits$q1))`, ordering a total of `r scales::comma(sum(quant$q1))` units.

# Order from Hong Kong

In order to refine the problem we then considered the situation in which there _were_ minimum order requirements. When ordering from Hong Kong there was a minimum order requirement of 600 units. This substantially changed the profit function and resulting optimisation problem.

## Define scenarios

When considering total profit from the order quantity, four scenarios had to be considered:

1. The true demand realisation was _less_ than the initial order quantity, $Q_j$;
2. The true demand realisation was greater than the initial order quantity but below a threshold (based on the minimum order requirement) that would trigger making a second order for that style at a later date;
3. The true demand realisation was greater than the initial order quantity plus the threshold value that would trigger making a second order for that style at a later date; and
4. The true demand realisation was greater than the initial order quantity plus the minimum order quantity.

## Define scenario profit outcomes

In each of the four scenarios, the profit formula would change slightly:

1. In the first scenario, Obermeyer would sell only the true demand realised, there would be an overstocking cost (based on the difference between the order quantity and the true demand), and the production cost would be dependent only on the initial order quantity;
2. In the second scenario, Obermeyer would sell the initial order quantity, there would be no overstocking cost and the production cost would be dependent only on the initial order quantity;
3. In the third scenario, Obermeyer would see the true demand realised, there would be an overstocking cost (based on the difference in the initial order quantity plus the minimum order quantity less the true demand), and the production cost would be dependent on the initial order quantity plus the minimum order quantity; and
4. In the fourth scenario, Obermeyer would sell the true demand realised, there would be no overstocking cost, and the production cost would be dependent only on the true demand realisation.

## Define scenario profit functions

In order to implement these four scenarios in the overall profit calculation, we defined four separate profit functions, one for each scenario (labelled $P_1$ to $P_4$):

\begin{equation} 
P_1 = p.d_{ij} + s.\max(Q_j - d_{ij}, 0) - c.Q_j
\end{equation}

\begin{equation}
P_2 = p.Q_j - c.Q_j
\end{equation}

\begin{equation}
P_3 = p.d_{ij} + s.\max(Q_j + q_{min} - d_{ij}, 0) - c.(Q_j + q_{min})
\end{equation}

\begin{equation}
P_4 = p.d_{ij} - c. d_{ij}
\end{equation}

Where $q_{min}$ is the minimum order quantity.

## Define scenario indicator functions

We then implemented four _indicator_ functions ($I_1$ to $I_4$) that could be used in the overall profit function to "switch" the four individual profit functions on/off depending on the comparison between the order quantity and the realised demand:

\begin{equation} 
I_1 = \dfrac{\max(Q_j - d_{ij}, 0)}{Q_j - d_{ij}}
\end{equation}

\begin{equation} 
I_2 = \dfrac{\max((Q_j + \frac{q_{min}(c-s)}{(p-s)}) - d_{ij}, 0)}{(Q_j + \frac{q_{min}(c-s)}{(p-s)}) - d_{ij}}
\end{equation}

\begin{equation} 
I_3 = \dfrac{\max((Q_j + q_{min}) - d_{ij}, 0)}{(Q_j - q_{min}) - d_{ij}}
\end{equation}

\begin{equation} 
I_4 = 1 - I_3
\end{equation}

In these equations $\frac{q_{min}(c-s)}{(p-s)}$ defines the threshold at which a new order will be placed if the realised demand exceeds the initial quantity ordered.

## Define overall profit function

Using the individual profit functions in conjunction with the indicator functions, we were then able to define an _overall_ profit function for this scenario:

\begin{equation}
Profit (\pi_q) = \sum_{j=1}^{10}\bigg[\frac{1}{n} \sum_{i=1}^{n} \Big[I_1.P_1 + (I_2 - I_1).P_2 + (I_3 - I_2).P_3 + I_4.P_4\Big]\bigg]
\end{equation}

We then translated this into a new optimisation problem that incorporated the minimum order requirements of producing in Hong Kong:

\begin{equation} \begin{split}
\max_{Q_j, z_j} \mathbb{E} (\pi_q) \\
\text{s.t.} \\
\sum_{j=1}^{10} Q_j \geq 10000 \\
Q_j \geq 0 \\
Q_j \geq q_{min}.z_j \\
Q_j \leq M.z_j \\
z_j \in \{0, 1\}
\end{split}
\end{equation}

Where $z_j$ is a binary variable indicating if style $j$ will be produced (which enables the minimum order quantities to be modelled).

## Hong Kong order results

The resulting solution from the `Excel` solver, including both order quantity and expected profit for each style is displayed in table 3. 

```{r show_q2}
quant %>% 
    select(1, 3) %>% 
    left_join(profits, by = c("style" = "style")) %>% 
    select(1, 2, 4) %>% 
    kable(col.names = c("Style", "Order Quantity", "Expected Profit ($)"),
          caption = "Table 3: Order quanties and expected profits for each style with Hong Kong minimum order requirements (600 units)",
          format.args = list(big.mark = ","),
          digits = 0)
```

Under this scheme, total profit was expected to be `r scales::dollar(sum(profits$q2))`, ordering a total of `r scales::comma(sum(quant$q2))` units.

## Ordering policy risk

Having determined the optimal order quantities for each style, we then quantified the risk associated with this ordering policy. We decided that the main risk was from overstocking - ordering an initial quantity higher than the true realisation of demand (as this would incur write downs and wasted production costs). Understocking on the initial order was less of a risk, as more could be produced later in the second order.

We therefore calculated, for each style's initial order quantity, the proportion of overstocking events based on the demand distributions generated from Obermeyer's forecasts. These proportions are displayed in table 4.

```{r overstock_risk_hk}
overstock_hk <- demand %>% 
    select(-2, -3, -4) %>% 
    gather(sim, value, -Style) %>% 
    left_join(quant %>% select(style, q2), by = c("Style" = "style")) %>% 
    mutate(overstock = q2 > value) 

overstock_hk %>% 
    group_by(Style) %>% 
    summarise(quantity = mean(q2),
              prop_overstock = mean(overstock)) %>% 
    mutate(prop_overstock = ifelse(quantity == 0, 0, prop_overstock),
           prop_overstock = 100*(prop_overstock)) %>% 
    arrange(Style) %>% 
    kable(col.names = c("Style", "Order Quantity", "Overstock Likelihood (%)"),
          caption = "Table 4: Overstocking likelihood for each style when ordering from Hong Kong.",
          digits = 0)
```

The overall (average) risk of overstocking was calculated to be `r scales::percent(mean(overstock_hk$overstock))`. 

In order to quantify this more concretely, we also assessed the distribution of profit values calculated based on the order quantities determined by the optimisation, and the realisation of demand in the simulations (as negative impacts on profit will be primarily caused by overstocking on the initial order). The standard deviation of profit for each style is displayed in table 5, and figure 2 shows the overall distribution of profit for each style.

```{r hk_profits}
hk_profits <- read_excel("./jim/optim.xlsx", sheet = "HKProfits") %>% gather(sim, value, -Style)

profits %>% 
    select(style, q2) %>% 
    left_join(hk_profits %>% group_by(Style) %>% summarise(sd = sd(value)), by = c("style" = "Style")) %>% 
    arrange(style) %>% 
    kable(col.names = c("Style", "Profit ($)", "Standard Deviation"),
          digits = 2,
          caption = "Table 5: Mean and standard deviation of profit expectation per style")
```

```{r show_hk_profit, out.height = 1000, out.width=800, fig.cap="Figure 2: Profit estimates for each parka style based on determined order quantites in Hong Kong. The shapes show the distribution of profit for each parka."}
hk_profits %>% 
    ggplot(aes(x = Style, y = value, fill = Style)) +
    geom_hline(yintercept = 0, colour = "grey") +
    geom_violin() +
    scale_y_continuous(labels = scales::comma) +
    scale_fill_brewer(palette = "Paired") +
    ylab("Profit ($)") +
    theme_jim +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.65))
```    

<br>

__The overall profit is `r scales::dollar(sum(profits$q2))` with a standard deviation of `r scales::comma(sd(profits$q2))` due to a `r scales::percent(mean(overstock_hk$overstock))` risk of overstocking.__

# Order from China

We also considered the same problem, but this time assumed that all styles were ordered from China, where the minimum order quantity was 1200 units. The same four scenarios defined for Hong Kong were also relevant to the analysis for ordering from China. As such, the overall optimisation problem remained the same for China as for Hong Kong, only with a different $q_{min}$ value of 1200.

## China order results

The resulting solution from the `Excel` solver, including both order quantity and expected profit for each style is displayed in table 6. 

```{r show_q3}
quant %>% 
    select(1, 4) %>% 
    left_join(profits, by = c("style" = "style")) %>% 
    select(1, 2, 5) %>% 
    kable(col.names = c("Style", "Order Quantity", "Expected Profit ($)"),
          caption = "Table 6: Order quanties and expected profits for each style with Chinese minimum order requirements (1200 units)",
          format.args = list(big.mark = ","),
          digits = 0)
```

Under this scheme, total profit was expected to be `r scales::dollar(sum(profits$q3))`, ordering a total of `r scales::comma(sum(quant$q3))` units.

## Ordering policy risk

We then quantified the risk associated with this ordering policy in the same was as for Hong Kong. The proportion of overstocking events based on the demand distributions generated from Obermeyer's forecasts are displayed in table 7.

```{r overstock_risk_china}
overstock_china <- demand %>% 
    select(-2, -3, -4) %>% 
    gather(sim, value, -Style) %>% 
    left_join(quant %>% select(style, q3), by = c("Style" = "style")) %>% 
    mutate(overstock = q3 > value) 

overstock_china %>% 
    group_by(Style) %>% 
    summarise(quantity = mean(q3),
              prop_overstock = mean(overstock)) %>% 
    mutate(prop_overstock = ifelse(quantity == 0, 0, prop_overstock),
           prop_overstock = 100*(prop_overstock)) %>% 
    arrange(Style) %>% 
    kable(col.names = c("Style", "Order Quantity", "Overstock Likelihood (%)"),
          caption = "Table 7: Overstocking likelihood for each style when ordering from China.",
          digits = 0)
```

The overall (average) risk of overstocking was calculated to be `r scales::percent(mean(overstock_china$overstock))`, slightly higher than for Hong-Kong. 

Similarly, we also assessed the distribution of profit values calculated for China based on the order quantities determined by the optimisation, and the realisation of demand in the simulations. The standard deviation of profit for each style is displayed in table 8, and figure 3 shows the overall distribution of profit for each style.

```{r china_profits}
china_profits <- read_excel("./jim/optim.xlsx", sheet = "ChinaProfits") %>% gather(sim, value, -Style)

profits %>% 
    select(style, q3) %>% 
    left_join(china_profits %>% group_by(Style) %>% summarise(sd = sd(value)), by = c("style" = "Style")) %>% 
    arrange(style) %>% 
    kable(col.names = c("Style", "Profit ($)", "Standard Deviation"),
          digits = 2,
          format.args = list(big.mark = ","),
          caption = "Table 8: Mean and standard deviation of profit expectation per style")
```

```{r show_china_profit, out.height = 1000, out.width=800, fig.cap="Figure 3: Profit estimates for each parka style based on determined order quantites in China. The shapes show the distribution of profit for each parka."}
china_profits %>% 
    ggplot(aes(x = Style, y = value, fill = Style)) +
    geom_hline(yintercept = 0, colour = "grey") +
    geom_violin() +
    scale_y_continuous(labels = scales::comma) +
    scale_fill_brewer(palette = "Paired") +
    ylab("Profit ($)") +
    theme_jim +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.65))
```    

<br>

__The overall profit is `r scales::dollar(sum(profits$q3))` with a standard deviation of `r scales::comma(sd(profits$q3))` due to a `r scales::percent(mean(overstock_china$overstock))` risk of overstocking. The average profit is lower than for Hong Kong, but the standard deviation is marginally smaller.__

# Operational recommendations

All in all Wally's job at Obermeyer is to use the demand forecasts to inform his order decisions at Obersport. One of Wally's biggest problem is that full production starts long before initial orders are placed. This leads to overstocking on less popular goods and a shortage on very popular goods. To improve performance based on forecasts Wally can make orders to Obersport based on tailored postponement. If the styles' demand variability is low, Wally can consider placing orders early on. If the styles' demand variability is high, Wally should design tailored postponement of the styles to cope with demand uncertainty. Furthermore, styles with higher demand uncertainty can be produced through Hong Kong, and vice versa. 

## Tailored Postponement

Wally can develop a procedure where styles can be made from a standard base product that can be ordered in bulk and then customised based when demand is certain, similar to his pre-ordering of Greige materials. This allows for the aggregation of demand across styles that have higher variability. We assume that aggregation will reduce variance, but increase production costs as well due to customisation later in the production time and increase production time. Additionally, it is also assumed that he is looking to improve performance in order to increase expected profits. 

This method can be done especially so for meeting second and third orders placed at Obersport, when it is closer to the delivery date to retailers. Assuming that storage costs is much less than the cost of selling overstocked goods at a large discount, it is preferable to adopt tailored postponement for meeting the last 20% and additional orders made by retailers. 

For both Hong Kong and China, we can consider the following options for aggregating demand:

1. aggregate high variability without considering quantity demanded
2. aggregate low demand quantity without considering variance
3. aggregate in a combination of variability + quantity demanded

The products with the highest standard deviation are: Anita - 2094, Daphne - 1394, Seduced - 1113 and Stephanie - 1048.

### Hong Kong Ordering Policy

There are four styles with an optimal quantity at/below 600: Stephanie, Teri, Isis and Gail. Gail and Stephanie at 0, and Isis and Stephanie at 600. And Teri, Isis and Daphne contribute most to the likelihood of overstocking. For HK, with a minimum requirement of 10,000, having some optimal quantities at zero contributes to the likelihood of overstocking on other styles.

Solutions are: group the products with highest standard deviation together, which are Anita, Daphne, Seduced and Stephane. To reduce likelihood of overstocking, styles of Teri, Isis and Daphne can be grouped together. To aim to produce all styles, Stephanie, Gail, Isis and Teri can be grouped together. All these solutions will reduce demand uncertainty and hence increase expected profits to an extent. 

### China Ordering Policy

Products with zero order quantity are: Gail, Isis, Entice, Teri and Stephanie. Styles with estimated demand being less than 1000 are Gail, Isis, Stephanie and Teri. Hence, grouping the five styles together will reduce demand uncertainty altogether. 

### Benefits

In general, tailored postponement reduces expected under and over stocking, which increases expected profits. In our case, the cost of understocking is zero and the cost of overstocking is high. The cost of overstocking will decrease for each style. 

To elaborate, the cost savings from reducing the number of overstocked goods materialises from reducing the amount of excess goods sold at large discounts.

Additional savings from reducing inventory level come from the reduction in inventory costs. Note that the supply chain process is approximately two years from the time of design to the time of delivery, which imply costly storage costs. Reducing demand uncertainty can reduce storage costs.

Postponement reduces pressures on productions at Obersport, and helps Obersport to meet retailer's demands/maintain good relationships with retailers.  

# Sourcing options

## Short Term

"Obermeyer competed by offering an excellent price/value relationship, where value was defined as both functionality and style". Apart from profit, this implies that trading relationships with retailers and quality of the products are important to the success of the company. Another consideration to take into account is trade relations between countries. Profit, quality, relationships, and economics are four criteria that Obermeyer should use to gauge which factories to source their products from. 

Objectively, the lower minimum requirement from Hong Kong factories yields a higher expected profit for Obermeyer. Based on the company's values, product quality, worker's conditions and delivery reliability, products sourced from Hong Kong are better. Although labour costs are more expensive, the overall expected profit is higher. When producing in Hong Kong, Obersport are better at dealing with uncertainty and are more likely to meet deadlines due to shorter production lines. In the short term, Hong Kong factories are better at managing inventory risks, responding to changes, and there is no risk of suffering from the import quota set by the US.

Moreover, if Wally adopts tailored postponement, this makes Hong Kong's flexibility, quality control and reliability more desirable for managing this process than China.

## Long Term

In the long term, it may be possible to take advantage of lower costs from producing in China if other risks reduce. Meaning if conditions change; when the China factories become better at dealing with uncertainty, and the US decides to change its regulations. If Obermeyer continues to grow with popularity and receives larger orders, then it should consider producing larger quantities through China. 

It may be possible that larger and less volatile products could be made in China, and higher volatility demand styles and tailored postponement orders be made through the Hong Kong factories. This allows each factory to play to their own advantages. If products from China fail to reach the US market due to the laws, Hong Kong factories can be used as a back up to reduce losses by producing more. This of course assumes non-binding minimum order constraints, this would naturally be doable when the company grows and has more sales.

## Conclusion

In conclusion, Hong Kong is recommended in the short term and Obermeyer should work towards production in China in the long term. 

