---
title: "BS1808 Logistics and Supply Chain Analytics Group Assignment Two"
author: "Jone Leung, Somto Okoye, Valentin Poirelle, Jin Anne Lee, Jim Leach, Niccolo Valerio"
date: "18 June 2016"
output:
  html_document:
    code_folding: hide
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
---

<br>
<br>
<p style="border:1.5px; border-style:solid; border-color:#000000; padding: 1em;"> This `HTML` report is best viewed using a modern web browser such as Mozilla Firefox or Google Chrome. It is also available on the [online repository](https://github.com/Jim89/lsca_group). Printing is possible but will not produce an optimal reading experience.</p>

```{r prep, echo = TRUE, message=FALSE}
# Set default knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center",
                      scipen = 999)

# Load packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(purrr)
library(readxl)

```

# Introduction

## Project overview

The overarching goal of this project is to optimise inventory and redesign the supply chain network of BioPharma, a chemical company. We use a combination of optimisation, heuristics and decision trees to evaluate improvements in order to make recommendations for courses of actions so that the company can cut costs and stay competitive in the global market.

In 2009, all six of BioPharma's plants maintained its capabilities for producing both Highcal and Relax; these chemicals can be shipped to any other parts of the world with additional costs attached. Furthermore, BioPharma faces import duties for all foreign goods entering a country, independent from plant origin. 

Based on the information given in tables, it is observed that

* Plants with higher fixed costs are Germany, Mexico and Japan.
* Plants with higher variable costs are Germany and Japan.
* Mexico and German plants have greater capacities. However, in 2009 not all plants operated at full capacitiy. Some regions such as US imported Highcal and Germany imported Relax from other plants.
* The plants in Mexico, US, Brazil and India is operating at full capacity. 
* Import tax into Europe, Japan and US is very low.

# Wiser on Hindsight: What could have been done in 2009

## The Optimisation Problem

Under the above conditions, the following optimisation problem is constructed to identify a more efficient use of resources.

__Decision Variables__

* $Q_{i,j,k}$ is the quantity of chemical $i$ to produce from plant $j$ for region $k$,
* $F_{all,j}$ is the fixed cost independent of chemical produced for plant $j$,
* $F_{i,j}$ is the fixed cost associated to producing chemical $i$ in plant $j$,
* $V_{i,j}$ is the total variable costs of raw materials and production costs,
* $T_{j,k}$ is the transportation costs for shipping from plant $j$ to region $k$, and
* $I_{j,k}$ is the import costs for importing from plant $j$ to region $k$

__Objective Function__

The objective function above is adjusted as follows: using the Brazil plant as follows, the costs function associated to Brazil is

minimise 

$\sum_{k=1}^6\sum_{j=1}^6 \sum_{i=1}^2 F_{all,j} + F_{i,j} + Q_{i,j,k}.(V_{i,j}+T_{j,k})( \textbf{1} +I_{j,k})$

where $\textbf{1}$ is the unit vector.

__Constraints__

* Non-negative quantities $Q_{i,j,k}$
* Maximum plant capacity for producing both chemicals
* Meeting sales and demand levels 

## Results

Biopharma should have utilised its resources in the following way:

```{r show_output}
# Set scipen
options(scipen = 999)

# Get raw demand data
output <- read_excel("optim1.xlsx", sheet = "Sheet1") %>% 
            # Set column names as the first two are not present in the Excel
            set_names(c("region", 
                        "chem", 
                        "brazil", 
                        "germany", 
                        "india", 
                        "japan", 
                        "mex", 
                        "us")) %>%
            # Fill in missing values with the value from the previous row for the 
            # region names which are missing
            mutate(region = zoo::na.locf(region))

# Pretty print the output
kable(output,
      col.names = c("Region", 
                    "Chemical", 
                    "Brazil", 
                    "Germany", 
                    "India", 
                    "Japan", 
                    "Mexico", 
                    "USA"),
      format.args = list(big.mark = ","),
      caption = "Table 1: Optimal Production Output in 2009")
```

The total cost for this new plan is USD1,372,432,000. The two plants who are serving their own regions in high quantities of chemicals are Germany and US, whereas the plants Brazil, Mexico and India are producing more evenly distributed quantities and serving at least two markets. 

BioPharma could have implemented production as shown above, at the cost of  USD1,337,340,000. The two plants serving their own regions in high quantities of chemicals are Germany and US, whereas the plants Brazil, Mexico and India are producing more evenly distributed quantities and serving at least two markets. 

The Japanese factory should have been idled because it was only producing 1mil units of Highcal for the local supply. The production of 1million units can be shifted to the plant in India, who is already producing units of Highcal for the Japanese market. This allows BioPharma to save on fixed costs, even though it is not the optimal plan. If the Japanese fatory were to be idled, only the general plant fixed costs will be incurred and the cost of this new plan will be USD1,325,340,000.

The results from the optimisation corroborates the serious consideration of shutting down the Japanese plant. 

# Looking ahead: Restructing the Global Supply Network

## Optimisation under options
In restructuring its global supply network structure, BioPharma has to consider exchange rate fluctuations and the option of shutting down factories simultaneously. The options available to the network design team are:

1. Keep global network with its current structure and capabilities.
2. Limiting the capability of some plants to producing only one chemical, where a plant is limited to producing only one chemical and it saves 80% of the fixed costs associated with the chemical that is no longer produced.
3. Closing down some plants, where closing down a plant eliminates all variable costs and saves 80% of annual fixed costs.

Assuming that demand in 2010 is stable and will be the same as in 2009: the new objective function is as follows:

minimise $(0.8B_0+0.2).F_{all,Brazil}+$
$(0.8B_1+0.2).F_{Brazil,Highcal}+\sum_{k=1}^6 Q_{Highcal,Brazil,k}.(V_{Highcal,Brazil}+T_{Brazil,k}).( \textbf{1} +I_{Brazil,k})$
$+(0.8B_2+0.2).F_{Brazil,Relax}+\sum_{k=1}^6 Q_{Relax,Brazil,k}.(V_{Relax,Brazil}+T_{Brazil,k}).( \textbf{1} +I_{Brazil,k})$

where 

* $B_0$ is the switch for closing or opening the entire Brazil factory
* $B_1$ is the switch for controlling the fixed costs for Highcal 
* $B_2$ is the switch for controlling the fixed costs for Relax 

under the additional conditions of

* $B_0 \geq B_1$, so that no Highcal is produced when the factory is shut
* $B_0 \geq B_2$, so that no Relax is produced when the factory is shut
* $MB_1 \geq \sum_{k=1}^6 Q_{Highcal,Brazil,k}$, so that no highcal is produced when the facilities are absent.
* $MB_2 \geq \sum_{k=1}^6 Q_{Relax,Brazil,k}$, so that no Relax is produced when the facilities are absent.

## Results

```{r show_output2}
# Get raw demand data
output2 <- read_excel("optim1.xlsx", sheet = "Sheet2") %>% 
            # Set column names as the first two are not present in the Excel
            set_names(c("region", 
                        "chem", 
                        "brazil", 
                        "germany", 
                        "india", 
                        "japan", 
                        "mex", 
                        "us")) %>%
            # Fill in missing values with the value from the previous row for the 
            # region names which are missing
            mutate(region = zoo::na.locf(region))

# Pretty print the output
kable(output2,
      col.names = c("Region", 
                    "Chemical", 
                    "Brazil", 
                    "Germany", 
                    "India", 
                    "Japan", 
                    "Mexico", 
                    "USA"),
      format.args = list(big.mark = ","),
      caption = "Table 2: Optimal Production Output with new Supply Network Design for 2010")

```

Based on the optimisation based on monetary criteria, BioPharma should compeletely shut down its Japanese plant. This is may possibly be attributed to the high fixed costs and low capacity of 10 million units incurred by the plant. Unless the high costs are justified by the plant being a technological leader and will be able to bring other external benefits in the long term to BioPharma, the Japanese plant can be shut and the technology can be transferred to other functioning plants. As a result, the Japanese market's demand for Highcal will be fulfilled by Brazil, Germany and India and the market demand for Relax by India. From Figure 6-18, it is observed that in 2009 Japan is already importing chemicals from other plants as its total demand of 15mil units exceeds its capacity of 10mil units. Furthermore, the plant was only producing a meagre 2mil units with full operational costs. 

In addition, it is suggested that Germany continue to produce only Highcal in the next year, and an extra 2 million kilograms for Japan. The other plants will continue to operate at full capacity with minor changes in the quantities of the chemicals. 

## Exchange Rates

The costs of doing business from a plant can be significantly lower due to weakened exchange rates. BioPharma as an international business will be greatly affected by these fluctuations and can opt to redistribute production to different plants based on exchange rates. The follow analysis is based on the assumption that BioPharma is a US company and is primarily interested in profits in US dollars as opposed to other currencies.

A decision tree is used to assess the risk of these fluctuations and to calculate the expected return of each plant. Assuming that the exchange rates in 2010 can fall or rise to any of the rates from 2004 to 2009 with equal probability, the following decision tree with expected costs is constructed: 

(insert picture of decision tree)

### Analysis

Exchange rates costs are expected to increase significantly at $30mil from Mexico and $12mil from India, and decrease $14mil from Brazil and $12mil from Germany. BioPharma faces a greater problem of rising costs from FX. In response, BioPharma can opt to shift Highcal production to Germany as it is not operating at full capacity. More specifically, Highcal exports to US can be managed by Germany. If necessary and if it becomes more cost effective due to weakening of exchange rates from Europe, Germany could open its Relax production capabilities to serve the European market for Relax. As for Brazil, it exports 1mil kg of Relax to Europe and 3mil kg of Highcal to Japan. Similarly, such productions can be shifted to other plants. 

This situation shows that the German plant's unused capactiy may not be as ineffective. The German plant gives BioPharma the flexibility to cope with unexpected economic environments, while maintaining its technological advancements.

Alternatively, these figures for the expected costs for each plant can be reintroduced into the optimisation problem in order to reestimate the supply chain network. BioPharma can also hedge against exchange rate risks through financial intermediaries.

#Scenario: Expansion Options

## The Optimisation Problem

In considering such options, this changes the optimisation by having: 

1. Additional binary variables of AB ($\textbf{A}$dditional capacity for $\textbf{B}$razil),  $AG$,  $AI$,  $AJ$,  $AM$ and  $AU$ to function as switches to allocate capacities for one factory. 
2. Constraint where additional capacity can only be added to one plant: $AB+AG+AI+AJ+AM+AU
<=1$

## Results

```{r show_output3}
# Get raw demand data
output3 <- read_excel("optim1.xlsx", sheet = "Sheet3") %>% 
            # Set column names as the first two are not present in the Excel
            set_names(c("region", 
                        "chem", 
                        "brazil", 
                        "germany", 
                        "india", 
                        "japan", 
                        "mex", 
                        "us")) %>%
            # Fill in missing values with the value from the previous row for the 
            # region names which are missing
            mutate(region = zoo::na.locf(region))

# Pretty print the output
kable(output3,
      col.names = c("Region", 
                    "Chemical", 
                    "Brazil", 
                    "Germany", 
                    "India", 
                    "Japan", 
                    "Mexico", 
                    "USA"),
      format.args = list(big.mark = ","),
      caption = "Table 3: Optimal Production Output with new Supply Network Design for 2010 with additional capacity")

```


Seeing that BioPharma is considering expanding one of its plant's capacity by 1mil kilograms at a cost of $3 million a year, they should expand the US plant. With the new capacity, it will produce an extra 1mil kilograms of Highcal for the domestic market, where Mexico will supply 1mil kilogram less to the US market. The total cost for this plan is $1,334,260,000, which is $3million dollars less than the orginal plan of $1,337,340,000. Hence, BioPharma will experience the greatest economies of scale if the money were invested in the US plant. 

Furthermore, seeing that this move reduces Mexico's production load for 2010, BioPharma will be safer from the changing exchange rates. 

# Scenario: A reduction of duties

## Results

Under the assumption that all import tariffs are removed, the new costs for BioPharma will be at USD1,267,200,000, which is more than $50mil less than all the other scenarios above. This further emphasises that import tariffs heavily affects the costs of production and distribution of the chemicals to different regions. 

```{r show_output4}
# Get raw demand data
output4 <- read_excel("optim1.xlsx", sheet = "Sheet4") %>% 
            # Set column names as the first two are not present in the Excel
            set_names(c("region", 
                        "chem", 
                        "brazil", 
                        "germany", 
                        "india", 
                        "japan", 
                        "mex", 
                        "us")) %>%
            # Fill in missing values with the value from the previous row for the 
            # region names which are missing
            mutate(region = zoo::na.locf(region))

# Pretty print the output
kable(output4,
      col.names = c("Region", 
                    "Chemical", 
                    "Brazil", 
                    "Germany", 
                    "India", 
                    "Japan", 
                    "Mexico", 
                    "USA"),
      format.args = list(big.mark = ","),
      caption = "Table 4: Optimal Production Output for 2010 without import tariffs")

```

Without import tariffs, optimal production quantity will depend more heavily on actual costs of production and transportation. We continue to see Germany increasing its production on Highcal only. It is observed that all plants except Brazil specialising in producing one chemical only, and each plant producing for a region outside of its own. Moreover, each country's demand is supplied by fewer plants.

# Not 100% yield


# What other factors to be considered when making your recommendations?
